---
title       : New avenues on visualization with R
subtitle    : R is more than statistics...
author      : Steve Vissault
job         : Research professional at UdS
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #
widgets     : [mathjax, quiz, bootstrap, interactive] # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3, libraries/leaflet, libraries/dygraphs]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
biglogo     : qcbs.png
assets      : {assets: ../../assets}

---

## R and the Web languages

RMarkdown + knitr = HTML + CSS + Javascript

- Created by Ramnath Vaidyanathan (McGill)
[http://slidify.org/](http://slidify.org/)

- Allows to generate slides in HTML/CSS/Javascript (Web lamguages)
- The new avenue for dynamic and interactive visualization

--- .segue bg:white

## Interactivity

---

## Hans Rosling and R

<div align="center">

```{r, results = 'asis', echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
plot(M1)
```
</div>

--- .segue bg:white

## HTML widgets

---

## HTML widget library

HTML widgets are interactive graphics made for the web. These are the main libraries available:

- [rCharts](http://rcharts.io/): interactive javascript visualizations from R
- [leaflet](https://rstudio.github.io/leaflet/): interactive maps
- [dygraphs](https://rstudio.github.io/dygraphs/): charting time series data
- [metricsgraphics](http://www.htmlwidgets.org/showcase_metricsgraphics.html): scatterplots, linegraphs and histograms
- [networkD3](http://christophergandrud.github.io/networkD3/): network graphs
- [DT](https://rstudio.github.io/DT/): print dataframes as html
- [threejs](http://www.htmlwidgets.org/showcase_threejs.html): 3d scatterplots and [globes](https://www.chromeexperiments.com/globe)
- [DiagrammeR](http://rich-iannone.github.io/DiagrammeR/): pretty diagrams

--- &radio2

## Quizz

Which of these two plots have a higher correlation?

1. A
2. B

*** =image

<img src=https://oli.cmu.edu/repository/webcontent/470835bf80020ca60018d5a6c359d34c/_u2_summarizing_data/_m2_examining_relationships/webcontent/linear1.gif>

*** .explanation

Both have the same correlation.

---
## rCharts

```{r rchart1, results = 'asis', comment = NA, message = F, echo = F}
library(rCharts)
n1 <- nPlot(mpg ~ wt, data = mtcars, type = 'scatterChart')
n1$show('inline')
```

Gallery: [http://rcharts.io/gallery/](http://rcharts.io/gallery/)

---

## leaflet

```{r echo=FALSE, message=FALSE}
library(knitr); library(htmlwidgets); library(dplyr)
read_chunk('html_widgets.R')
```

```{r, 'leaflet1', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/leaflet1.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## dygraphs

```{r, 'dygraphs1', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/dygraphs1.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## dygraphs (cont)

```{r, 'dygraphs2', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/dygraphs2.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## dygraphs (cont)

```{r, 'dygraphs3', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/dygraphs3.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## dygraphs (cont)

```{r, 'dygraphs4', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/dygraphs4.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## metricsgraphics

```{r, 'metricsgraphics1', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/metricsgraphics1.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## metricsgraphics (cont)

```{r, 'metricsgraphics2', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/metricsgraphics2.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## metricsgraphics (cont)

```{r, 'metricsgraphics3', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/metricsgraphics3.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## metricsgraphics (cont)

```{r, 'metricsgraphics4', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/metricsgraphics4.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## metricsgraphics (cont)

```{r, 'metricsgraphics5', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/metricsgraphics5.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## metricsgraphics (cont)

```{r, 'metricsgraphics6', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/metricsgraphics6.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## networkD3

```{r, 'networkD31', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/networkD31.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## networkD3 (cont)

```{r, 'networkD32', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/networkD32.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## DT

```{r, 'datatable1', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/dt1.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## threejs

```{r, 'threejs1', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/threejs1.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## threejs (cont)

```{r, 'threejs2', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/threejs2.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## DiagrammeR

```{r, 'diagrammer1', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/diagrammer1.html" width=100% height=100% allowtransparency="true"> </iframe>')
```

---

## DiagrammeR (cont)

```{r, 'diagrammer2', echo=FALSE, warning=FALSE,cache=FALSE,results='asis'}
cat('<iframe src="./assets/widgets/diagrammer2.html" width=100% height=100% allowtransparency="true"> </iframe>')
```
